---
title: "ULTrA Measurement Invariance"
output: html_document
---

Import data if starting from here
```{r}
library(lavaan)
library(readr)
setwd("~/Desktop")
data <- read_csv("ULTRAdata_combined.csv")
```


Set up the model
```{r}
mod <- 'growth =~ Growth_01 + Growth_02 + Growth_03 + Growth_04 + Growth_05 + Growth_06 + Growth_07 + Growth_08 + Growth_09 + Growth_10
fixed =~ Fixed_01 + Fixed_02 + Fixed_03 + Fixed_04 + Fixed_05 + Fixed_06 + Fixed_07 + Fixed_08 + Fixed_09 + Fixed_10 + Fixed_11
universal =~ Universal_01 + Universal_02 + Universal_03 + Universal_04 + Universal_05 + Universal_06 + Universal_07 + Universal_08 + Universal_09 + Universal_10 + Universal_11
nonuniversal =~ NonUniversal_01 + NonUniversal_02 + NonUniversal_03 + NonUniversal_04 + NonUniversal_05 + NonUniversal_06 + NonUniversal_07 + NonUniversal_08 + NonUniversal_09 + NonUniversal_10 + NonUniversal_11 + NonUniversal_12
brilliance =~ Brilliance_1 + Brilliance_2 + Brilliance_3 + Brilliance_4 + Brilliance_5 + Brilliance_6
mindset =~ growth + fixed
universality =~ universal + nonuniversal'
```

Estimate the null model. The null model does not include any differences across groups
```{r}
NoGroups<-cfa(mod,data,estimator="MLR", meanstructure=T)
summary(NoGroups,standardized=T,fit.measures=T)
```


Get the residuals of this model
```{r}
residuals <- residuals(NoGroups, type = "standardized")
write.csv(residuals,"finalmod_residuals.csv")
```

Check modification indices for 4 factor, 2 higher order factor model to identify poorly fitting items
```{r}
#calculate modification indices
mod_ind <- modificationindices(NoGroups, sort.=TRUE, minimum.value=3)
write.csv(mod_ind,"finalmod_ModInd.csv")
```




Multiple Group comparison with gender
```{r}
data$Gender <- as.factor(data$Gender)

GenderMod<-cfa(mod,data,estimator="MLR", group="Gender")
summary(GenderMod, fit.measures=T)
```

Ask Nate - Lavaan warning: Group variable 'Gender" contains missing values
What is the default action? Drop? Should I indicate drop or FIML?

Compare the null and gender models
```{r}
anova(NoGroups,GenderMod)
```

Multiple Group comparison with RaceEth
comparing individuals who selected "white" as an identity with those who did not
```{r}
RaceEth_White<-cfa(mod,data,estimator="MLR", group="White")
summary(RaceEth_White, fit.measures=T)
```

compare the null and the RaceEth_White models
```{r}
anova(NoGroups, RaceEth_White)
```

```{r}
RaceEth_URM<-cfa(mod,data,estimator="MLR", group="URM")
summary(RaceEth_URM, fit.measures=T)
```


```{r}
anova(NoGroups, RaceEth_URM)
```

Multiple Group comparison with learning disability: 2 comparisons
first comparison: Any disabilities (T) vs. no disabilities (F)
```{r}
DisabMod<-cfa(mod,data,estimator="MLR", group="disab")
summary(DisabMod, fit.measures=T)
```

Compare the null and disability models
```{r}
anova(NoGroups,DisabMod)
```

Multiple Group comparison with learning disability: 2 comparisons
second comparison: Specific learning disabilities (T) vs. not specific learning disabilities (F)
```{r}
LDMod<-cfa(mod,data,estimator="MLR", group="LD")
```
Covariance matrix is not positive definite, cannot make this comparison.


Multiple Group comparison with generation
```{r}
data$Generation <- as.factor(data$Generation)

GenerationMod<-cfa(mod,data,estimator="MLR", group="Generation")
summary(GenerationMod, fit.measures=T)
```

```{r}
anova(NoGroups,GenerationMod)
```


Multiple Group comparison with Language
```{r}
data$Language <- as.factor(data$Language)

LangMod<-cfa(mod,data,estimator="MLR", group="Language")
summary(LangMod, fit.measures=T)
```


```{r}
anova(NoGroups, LangMod)
```



Multiple Group comparison with Institution type
```{r}
data$instcc <- FALSE
data$instcc[data$insttype=="CC"] <- TRUE
data$instcc <- as.factor(data$instcc)

instccMod<-cfa(mod,data,estimator="MLR", group="instcc")
summary(instccMod, fit.measures=T)
```



```{r}
anova(NoGroups, instccMod)
```


```{r}
data$inst4yr <- FALSE
data$inst4yr[data$insttype=="Baccalaureate"] <- TRUE
data$inst4yr[data$insttype=="Masters"] <- TRUE
data$inst4yr[data$insttype=="Doctoral"] <- TRUE
data$inst4yr <- as.factor(data$inst4yr)

inst4yrMod<-cfa(mod,data,estimator="MLR", group="inst4yr")
summary(inst4yrMod, fit.measures=T)
```


```{r}
anova(NoGroups, inst4yrMod)
```


```{r}
#collapse HRA & VHRA because there are very few responses from HRA
data$insttype[data$insttype=="VHRA"] <- "HRA"

data$insttype2 <- NA
data$insttype2[data$insttype=="HRA"] <- "HRA"
data$insttype2[data$insttype=="Doctoral"] <- "4yr"
data$insttype2[data$insttype=="Masters"] <- "4yr"
data$insttype2[data$insttype=="Baccalaureate"] <- "4yr"
data$insttype2[data$insttype=="CC"] <- "CC"
data$insttype2 <- as.factor(data$insttype2)

insttypeMod<-cfa(mod,data,estimator="MLR", group="insttype2")
summary(insttypeMod, fit.measures=T)
```


```{r}
anova(NoGroups, insttypeMod)
```

Institution population
```{r}
data$instpop <- as.factor(data$instpop)

popMod<-cfa(mod,data,estimator="MLR", group="instpop")
summary(popMod, fit.measures=T)
```

```{r}
anova(NoGroups, popMod)
```



Discipline 
biology
```{r}
data$bio <- as.factor(data$bio)

bioMod<-cfa(mod,data,estimator="MLR", group="bio")
summary(bioMod, fit.measures=T)
```

```{r}
anova(NoGroups, bioMod)
```


chemistry
```{r}
data$chem <- as.factor(data$chem)

chemMod<-cfa(mod,data,estimator="MLR", group="chem")
summary(chemMod, fit.measures=T)
```

```{r}
anova(NoGroups, chemMod)
```



physics
```{r}
data$phys <- as.factor(data$phys)

physMod<-cfa(mod,data,estimator="MLR", group="phys")
summary(physMod, fit.measures=T)
```

```{r}
anova(NoGroups, physMod)
```



math
```{r}
data$math <- as.factor(data$math)

mathMod<-cfa(mod,data,estimator="MLR", group="math")
summary(mathMod, fit.measures=T)
```

```{r}
anova(NoGroups, mathMod)
```
